\section{Optics Overview \label{ch2:opticsOverview}}
    As electromagnetic waves travel through a medium, these waves induce a
    polarization and magnetization on the medium's molecules; leading to the
    formation of dipoles. These dipoles generate their own electric and
    magnetic waves, representing bound charges and bound currents,
    respectively. Consequently, the newly formed wave arising from the combined
    effects of polarization and magnetization, interacts with the incident wave
    of identical frequency but varying propagation velocities \cite{Griffiths2017, Jackson1998}. \todo{Make a figure explaining EM waves and dipoles}

    This varying in propagation velocity can be quantify
    by the index of refraction given in \cref{eq:generalIndexOfRefraction}.
    \begin{equation}\label{eq:generalIndexOfRefraction}
        n = \frac{c_0}{c_m} \equiv \sqrt{\frac{\mu_m\epsilon_m}{\mu_0\epsilon_0}}
        \approx \sqrt{\frac{\epsilon_m}{\epsilon_0}}
    \end{equation}

    \Cref{fig:ch2LightRefraction} shows a picture of a material bending a
    beam of light. Inside the material the speed of light is lower than outside
    the material. The same effect takes place when a beam of light travels
    across a denser medium such as a boundary layer.

    \pic{0.6}{chapter2/refractionOfLight}{A ray of light refracted in a
        plastic block}{fig:ch2LightRefraction}

    The speed light in a thinner medium is larger than in a denser medium \cite{Feynman2011b}. Thus
    the speed of light in a medium is inversely proportional to the medium's
    density \cref{eq:densitySpeedOfLightProportionaly}.
    \begin{equation}\label{eq:densitySpeedOfLightProportionaly}
        \rho_{m} \propto \frac{1}{c_m}
    \end{equation}

    As a vehicle moves through a medium, it generates pressure waves. When the
    vehicle travels at speeds faster than the speed of sound in that medium,
    these pressure waves cannot move ahead of the vehicle and start to compress
    and bunch together near the leading edge. This compression creates a sudden
    change in pressure and density known as a shock wave. Shock waves are
    characterized by an abrupt and nearly discontinuous change in the
    properties of the medium, such as pressure, temperature, and density, which
    travel through the medium at supersonic speeds.\\

    \cref{fig:ch2ShockWaves} illustrates how the pressure wave expansion changes with varying Mach numbers. Shock waves begin to form when the Mach number exceeds unity, resulting in different fluid properties, such as density, before and after the shock. This density gradient affects the index of refraction.
    \pic{1.1}{chapter2/shockWaves}{Shock waves formation}{fig:ch2ShockWaves}

    Optical wave propagation through an inhomogeneous medium where the index of
    refraction varies, results in wavefront deformation, as illustrated in
    \cref{fig:wavefrontDistortion}. This deformation can significantly degrade the performance of optical systems. However, it can also be leveraged as a visualization technique, such as the Schlieren method, used by experimental fluid researchers. This method exploits variations in the refractive index to visualize fluid flow, density gradients, and other phenomena in transparent media.\\

    It is important to distinguish between the
    term "near field" as used in this context and its use in physical optics. In
    the current context, "near field" refers to aberrating fluid structures that
    are located very close to the exit aperture of the optical system. In contrast,
    in physical optics, the "near field" refers to a region where the Fresnel
    approximations are applicable, but the Fraunhofer approximations are
    not \cite{Jumper2001}.
    \pic{0.9}{chapter2/wavefrontDistortion}{Planar optical wavefront distorted by a
    variant index of refraction
    flowfield\cite{Jumper2001}}{fig:wavefrontDistortion}

    In this context, short-path (near-field) aberration is commonly referred to as
    \textit{aero-optics}, which deals with the optical distortions caused by turbulent
    airflows near the optical system, such as those experienced by airborne or
    ground-based sensors. On the other hand, long-path aberrations, which occur
    over extended distances through the atmosphere, are generally referred to as
    "atmospheric propagation" effects. These long-path distortions are typically
    due to atmospheric turbulence, temperature gradients, and other environmental
    factors that cause fluctuations in the index of refraction over the optical
    path \cite{Jumper2001}.\\

    Optical aberrations can be measured in terms of the \gls{OPL}, given in
    \cref{eq:OPL}. The \gls{OPL} is a measure of the effective distance that light
    travels in a medium, taking into account both the physical distance and the
    refractive index of the medium. The \gls{OPL} determines the phase change that light
    undergoes as it propagates through a medium \cite{Jenkins1976}. In other words, it is the "effective" distance light travels when considering how different materials slow down the speed of light relative to its speed in a vacuum.
    \begin{equation}\label{eq:OPL}
        OPL(t,x) = \int_{y_1}^{y_2} n(t,x,y)dy
    \end{equation}

    Instead of measuring the absolute \gls{OPL}, only the relative difference in
    \gls{OPL} across the aperture is important. The \gls{OPD} is given by
    \cref{eq:OPD}. The \gls{OPD} directly reflects the variations of the
    wave-front phase errors \cite{Wang2007}.
    \begin{equation}\label{eq:OPD}
        OPD(t,x) = OPL(t,x) - \overline{OPL}(t)
    \end{equation}
    Note: $\overline{\Parenthesis{\;}}$ denotes the spatial average over the
    aperture.\\ 

    \todo{Connect this with the following text}

    However, all these \gls{AO} properties are affected by nonequilibrium
    effects. Mackey \cite{Mackey2018, Mackey2019, Mackey2019a} demonstrated that there
    is a discrepancy in the \gls{AO} such as the index of refraction between a
    real and a perfect gas. \\

    The culprit for this discrepancy is the polarizability, which refers to a molecule's tendency to develop a
    temporary dipole moment when exposed to an electric field. In other words,
    polarizability measures how easily a molecule's electron cloud can be
    distorted or shifted in response to an electric field. The greater the
    polarizability, the more easily the electron cloud can be distorted.
    \cref{fig:ch2Polarizability} shows the polarizability of a molecule when
    an electric field is applied to it.
    
    \pic{1}{chapter2/polarizability}{Polarizability, the tendency of a
    molecule to form a dipole moment when an electric field is
    applied}{fig:ch2Polarizability}

    The polarizability may be usually separated into three distinct parts:
    electronic, ionic and dipolar as shown in
    \cref{fig:ch2FrequencyDependencePolarizability}. The electronic
    polarizability arises from the displacement of the electron shell relative
    to the nucleus. The ionic polarizability arises from the displacement of
    charged ions with respect to other ions. The dipolar polarizability arises
    from molecules with a permanent electric dipole moment that can change
    orientation in an applied field \cite{Kittel2004}.

    \pic{1.7}{chapter2/frequencyDependencePolarizability}{Frequency of the
    several contributions to
    polarizability}{fig:ch2FrequencyDependencePolarizability}

    Traditionally the polarizability of air it is thought to be only a function of
    the frequencies. However, for the cases of hypersonic flows this is
    not the case. Hohm \cite{Hohm1986} showed a temperature dependency on
    polarizabilty using interfreometric measuremnt. Kerl \cite{Kerl1992} used
    the results of Hohm used a fitting \cref{eq:kerlFitting} to show a
    polarizabilty dependence in polarizability. \Cref{fig:kerlPolarizabilityT}
    shows these results using constants in \cref{tab:kerlConstants}.
    
    \begin{equation}\label{eq:kerlFitting}
        \alpha(\omega,T) = \frac{\alpha(0,0)}{1 -
        \Parenthesis{\frac{\omega}{\omega_0}}^2} \Parenthesis{1 + bT + cT^2}
    \end{equation}
    
    \begin{table}[H]
        \makebox[\linewidth][c]{
            \begin{tabular}{|c|c|c|c|c|} 
                \hline
                molecule & $\alpha_0\times10^{30}\Units{m^3}$ &
                $\omega_0\times10^{16}\UnitsFrac{rads}{sec}$ &
                $b\times10^{-6}\UnitsFrac{1}{K}$ &
                $c\times10^{-9}\UnitsFrac{1}{K}$ \\
                \hline\hline
                $N2$ & $1.7406$ & $2.6049$ & $1.8$ & -- \\ \hline
                $O2$ & $1.5658$ & $2.1801$ & $-2.369$ & $8.687$ \\ \hline
                $Air$ & $1.6970$ & $2.47044$ & $10.6$ & $7.909$ \\ \hline
            \end{tabular}
        }
            \caption{Constant used in
            \cref{eq:kerlFitting}}\label{tab:kerlConstants}
    \end{table}


    \pic{0.8}{chapter2/polKerl_633nm}{Polarizability for a wavelength of
    $633\Units{nm}$}{fig:kerlPolarizabilityT}

    Tropina \cite{Tropina2018, Tropina2020} and Anaya \cite{Anaya2023} have
    demonstrated an influence of vibrational energy modes on polarizability.
    Kerl \cite{Hohm1986} and Buldakov \cite{Buldakov2000a} have demonstrated a temperature dependency in the polarizability. 


\iffalse
    The \gls{ZPE} was calculated using \cref{eq:zpe} provided in
    \cite{Irikura2007}. The \gls{ZPE} is the lowest possible energy that a
    quantum mechanical system may have. It has to be noted that this is only
    possible to be obtained for diatomic molecules, because monatomic
    molecules only have translational energy modes \cite{Eisberg1985}. 
    \begin{equation}\label{eq:zpe}
        ZPE = \frac{\omega_e}{2} - \frac{\omega_ex_e}{2} + \frac{\omega_ey_e}{8} +
        \frac{B_e}{4} + \frac{\alpha_e\omega_e}{12B_e} +
        \frac{\alpha_e^2\omega_e^2}{144B_e^3}
    \end{equation}

    The \gls{ZPE} is given on units of wavenumber sometimes called
    \textit{kayser}. This unit represents the number of wavelengths per
    centimeter and it is often used in spectroscopy \cite{Gauglitz2003}. The
    \gls{ZPE} can be converted to
    the ground-state angular frequency by using
    \cref{eq:zpeToRotationalFrequency}, and the ground state energy on units of
    joules is found using \cref{eq:groundStateEnergy}; results from these
    equations are giving
    on \cref{tab:groundStateAngularFrequency}.
    \begin{subequations}\label{eq:waveNumberConversions}
        \begin{align}
            \omega_0 &= 2\pi \times ZPE \times c_0 \times
            10^{-2}\UnitsFrac{rads}{s}
            \label{eq:zpeToRotationalFrequency}\\
            E_0 &= \hbar \omega_0 \label{eq:groundStateEnergy}
        \end{align}
    \end{subequations}
    \begin{table}[H]
        \makebox[\linewidth][c]{
            \begin{tabular}{|c|c|c|}
                \hline
                Molecule & $\omega_0 \times 10^{14}\UnitsFrac{rad}{s}$
                & $E_0 \times 10^{-20}\Units{J}$ \\
                \hline\hline
                $NO+$ & $2.231$ & $2.353$ \\ \hline
                $N2+$ & $2.071$ & $2.184$ \\ \hline 
                $O2+$ & $1.787$ & $1.885$ \\ \hline
                $NO$ & $1.787$ & $1.885$ \\ \hline
                $N2$ & $2.215$ & $2.336$ \\ \hline
                $O2$ & $1.483$ & $1.564$ \\ \hline 
            \end{tabular}
        }
            \caption{Ground-state properties for diatomic molecule\label{tab:groundStateAngularFrequency}}
    \end{table}
\fi



