\section{Background \label{ch1:background}}
    Investigations of \gls{AO} effects at low enthalpy at subsonic and
    supersonic speeds have been conducted by many authors. Sontag
    \cite{Sontag2020} performed measurements in a subsonic turbulent boundary
    layer at different spatial distributions. \\

    Kanlensky \cite{Kalensky2023} performed an analytical analysis of \gls{OPD}
    across a shock wave using Rankine-Hugoniot conditions for a supersonic
    flow, and compared his analysis with data from a Shack-Hartmann wavefront
    sensor. Fassler \cite{Fassler2024} performed a experimental study on a supersonic mixing
    layer. Ding \cite{Ding2024} performed a computational analysis using
    \gls{CFD} to study the effects of supersonic turbulent shear layers in
    \gls{AO}.  Gupta et.al. \cite{Gupta2020} used an analytical approach to the
        effects of a shock wave in the index of refraction for a supersonic
        flow.  \\

    Some applied
    work studying the influence of a seeker head on a hypersonic flow was
    conducted by Li \cite{Li2023}.  In this study, Li
        investigated the \gls{BSE} and \gls{OPD} 
        at various seeker-cone angles (ranging from $10^{\circ}$ to
        $60^{\circ}$) and \gls{LOS} angles (ranging from $5^{\circ}$
        to $60^{\circ}$) for a Mach 5 flow using \gls{RANS} simulations, without considering nonequilibrium
        effects. Li's work covers Quadrant I in \Cref{tab:ch1AeroOpticalFidelities}. Additionally, an experimental study of
        optical distortions in a ground-test facility at three different Mach
        numbers ($9$, $12$, and $15$) was performed by Pallotta
        \cite{Pallotta2025}, who found that the maximum distortion occurred at
        Mach 9. Pallotta's work covers Quadrant II in \Cref{tab:ch1AeroOpticalFidelities}. Lynch \cite{Lynch2022} performs an
        experimental study of hypersonic turbulent boundary layers but does not
        consider high enthalpy effects, this work cover covers Quadrant II in
        \Cref{tab:ch1AeroOpticalFidelities}. Castillo
        \cite{CastilloGomez2023a}
        performed an \gls{AO} study on a backward-facing step and a
        compression ramp for a Mach 2 flow using a \gls{LES};
        the results from the simulation were compared against experimental
        results obtained in the Tri-Sonic Wind Tunnel at Notre Dame University.
        On this study Castillo calculated the \gls{OPD} and
        showed optical distortions downstream of the reattachment. Castillo's
        work covers Quadrant II in \Cref{tab:ch1AeroOpticalFidelities}.\\

        A conference paper focusing on Quadrant III was published by Liza et
        al. \cite{Liza2023}. In this paper, the authors examined the impact of
        high temperatures and nonequilibrium conditions on polarizability.
        Additionally, they investigated the effects of Mach number, turbulence,
        and chemistry modeling on optical properties, including the index of
        refraction and the dielectric constant of air. \\

        Some work at high speeds flows using \gls{DSMC} is performed by Anaya
        \cite{Anaya2023} et. al., on this work, the authors investigated the
        index of refraction at very high mach numbers (mach $15$ and mach
        $20$) and showed that the index of refraction changes with the amount
        of electrons in the flow.
