\newpage
\section{Dissertation Outline\label{ch1:dissertationOutline}}
Work in the realm of turbulence effects in \gls{AO} at subsonic and supersonic
conditions has been extensively studied \cite{Mathews2019,Wang2007}, and some
investigation of hypersonic flows for a five-species gas has been performed by
Mackey \cite{Mackey2018,Mackey2019,Mackey2019a}. All of this prior work uses a
dilute formulation of the index of refraction; however, none of these studies
have examined whether this formulation remains sufficiently accurate under
hypersonic conditions. In addition, none of these studies have considered an
eleven-species gas, nor have they explored internal state-specific or
species-specific formulations.\\

This dissertation investigates the effects of high-enthalpy flows on \gls{AO}
phenomena using high-fidelity \gls{CFD} simulations to resolve the relevant
thermal and chemical nonequilibrium in hypersonic flows. An open-source package,
\gls{HAOT}, is developed to post-process and analyze the optical distortion
characteristics extracted from the \gls{CFD} results. The central question this
dissertation aims to address is: \textit{To what extent do high-enthalpy flow
conditions influence the \gls{AO} properties of the medium?} \\

\Cref{ch:ch2} will present the fundamental theoretical background
necessary to understand the field of \gls{AO}, including key physical
concepts, governing equations, and relevant literature. This chapter will
establish the foundation for the subsequent analysis by reviewing prior
research and highlighting gaps that this dissertation aims to address. \\

\Cref{ch:ch3} will focus on the computational fluid dynamics
(\gls{CFD}) tools used to perform the simulations. It will provide an overview
of the selected solvers, numerical methods, and turbulence models. It will also
introduced the \gls{HAOT} package package developed in this dissertation. This
section will detail the main functionalities of \gls{HAOT}, including its implementation, governing
equations, and computational framework, demonstrating how it extends existing
\gls{AO} analysis capabilities. \\

\Cref{ch:ch4} will present case studies that combine the \gls{CFD}
results with the \gls{HAOT} package to analyze key \gls{AO} phenomena. This
chapter will explore the impact of turbulence, nonequilibrium effects, and
refractive index variations on optical wave propagation in hypersonic flows. \\

Finally, \Cref{ch:ch5} will summarize the key findings of this
dissertation, discussing their implications for \gls{AO} analysis in
hypersonic regimes. It will also outline potential future research directions
based on the results obtained. \\
