    \section{Motivation\label{ch1:motivation}}
        Several reports in the classified and unclassified
        \cite{Jones2009, ChiefScientistAirForce2010, Stone2022} environment have stated
        the concern of \gls{AO} effects at hypersonic speeds to be of
        paramount importance for national security. Applied work in this field
        is not only being done by national laboratories such as \gls{LLNL},
        \gls{JHU}-\gls{APL}, \gls{LANL} but also by the
        \gls{DoD} contractors such as Lockheed Martin Corp.,
        Northrop Grumman Corp., Raytheon Technologies. As expected most of
        this work is limited in the open literature. However, work that
        investigates the effect of optical properties in a hypersonic
        environment is lacking and there are many fundamental phenomenons such
        as index of refraction, that needs to be better understood.\\

        A study examining the influence of a seeker head
        on hypersonic flow was conducted by Li \cite{Li2023}. In this study, Li
        investigated the \gls{BSE} and \gls{OPD} 
        at various seeker-cone angles (ranging from $10^{\circ}$ to
        $60^{\circ}$) and \gls{LOS} angles (ranging from $5^{\circ}$
        to $60^{\circ}$) for a Mach 5 flow using \gls{RANS} simulations, without considering nonequilibrium
        effects. Li's work covers Quadrant I in \cref{tab:ch1AeroOpticalFidelities}. Additionally, an experimental study of
        optical distortions in a ground-test facility at three different Mach
        numbers ($9$, $12$, and $15$) was performed by Pallotta
        \cite{Pallotta2025}, who found that the maximum distortion occurred at
        Mach 9. Pallotta's work covers Quadrant II in \cref{tab:ch1AeroOpticalFidelities}. Lynch \cite{Lynch2022} performs an
        experimental study of hypersonic turbulent boundary layers but does not
        consider high enthalpy effects, this work cover covers Quadrant II in
        \cref{tab:ch1AeroOpticalFidelities}. Castillo
        \cite{CastilloGomez2023a}
        performed an \gls{AO} study on a backward-facing step and a
        compression ramp for a Mach 2 flow using a \gls{LES};
        the results from the simulation were compared against experimental
        results obtained in the Tri-Sonic Wind Tunnel at Notre Dame University.
        On this study Castillo calculated the \gls{OPD} and
        showed optical distortions downstream of the reattachment. Castillo's
        work covers Quadrant II in \cref{tab:ch1AeroOpticalFidelities}\\.

        \Cref{fig:ch1strategicWeapon} illustrates the notional flight paths for
        various long-range weapons. Accurate target detection is of paramount
        importance in these scenarios. Cruise missiles generally travel at
        subsonic speeds, whereas ballistic missiles and boost-glide vehicles
        can reach speeds in the hypersonic regime. At these hypersonic
        velocities, the vehicles are subject to intense aerodynamic heating and
        dynamic pressure, resulting in complex hypersonic flow fields around
        the vehicle. These conditions can significantly degrade seeker
        performance, impacting sensors' ability to lock onto targets due to
        thermal interference, signal distortion and change in \gls{EM} properties. 
        Advanced guidance systems must compensate for these factors to maintain
        precision in target acquisition and engagement.
        \pic{0.17}{chapter1/strategicWeapons}{Notional flight paths of
        hypersonic boost-glide missiles, ballistic missiles, and cruise
        missiles. (\gls{CSBA} graphic)}{fig:ch1strategicWeapon}

        In addition, hypersonic vehicles can be detected by enemy ground-based
        radar systems. \Cref{fig:radarStrategicWeapons} illustrates the flight
        trajectories of an \gls{ICBM} and a \gls{HGV}. It is evident that
        \glspl{ICBM} are more easily detected compared to \glspl{HGV} primarily
        due to their higher apogee (the point of maximum altitude) during
        flight. \glspl{ICBM} typically travel through space along a ballistic
        arc, reaching altitudes that expose them to long-range radar systems
        for an extended period. \\

        In contrast, \glspl{HGV} operate at lower altitudes within the
        atmosphere, following a maneuverable, non-ballistic trajectory. This
        allows them to remain below the radar horizon for a longer duration,
        thereby reducing their detectability and increasing their
        survivability. However, because \glspl{HGV} fly within the denser
        layers of the atmosphere at extremely high velocities, they are subject
        to significant aerodynamic heating, turbulence, and real gas
        effects—all of which can degrade the performance of onboard optical
        sensors and seekers. \\

        Maintaining precise and accurate \gls{GNC} under such extreme
        conditions is critical to mission success. The ability of these systems
        to rapidly adapt to a dynamically changing environment, maintain sensor
        fidelity, and accurately strike their target despite \gls{AO} 
        distortions is essential for the operational effectiveness of
        hypersonic weapons.
        %https://news.usni.org/2023/01/27/report-to-congress-on-hypersonic-missile-defense-2
        \pic{0.9}{chapter1/radarStrategicWeapons}{Hypersonic weapons}{fig:radarStrategicWeapons}

        A crude approximation for the index of refraction in the atmosphere at
        radio frequencies was proposed by Smith and Weintraub \cite{Smith1953}
        and it is given on \cref{eq:crudeIndexApproximation}. Where $K_1 =
        79\UnitsFrac{K}{mB}$, $K_2=4800\Units{K}$, $e$ is the partial pressure
        of water vapor in millibars. 
        \begin{equation}\label{eq:crudeIndexApproximation}
            n(h) \approx 1 + \frac{K_1}{T(h)} \Parenthesis{ p(h) +
            K_2\frac{e(h)}{T(h)}} 
        \end{equation}
        \Cref{fig:ch1AtmosphericOptics} illustrates the index of refraction
        as a function of altitude for a \textit{blue-sky} scenario. The most
        drastic change in the index of refraction occurs at approximately
        $15\Units{km}$ above sea level, which is in the tropopause, near the
        boundary where the troposphere ends and the stratosphere begins. This
        is also the altitude at which commercial planes and jets typically fly.
        It is a critical region where sensor accuracy is especially important.
        \pic{0.85}{chapter1/atmosphericOptics}{Atmospheric index of
        refraction}{fig:ch1AtmosphericOptics}

        However, the index of refraction consists of both a real and a complex
        component, as expressed in \cref{eq:totalIndexOfRefraction}. The real
        part, $n$, governs the phenomenon of bending or refraction of
        light as it passes through a medium, while the complex part, $k$, is
        associated with attenuation or absorption of the wave as it
        propagates. The attenuation arises due to energy dissipation within the
        medium, which is particularly relevant in plasmas, where ionization
        effects contribute to optical losses. 
        \begin{equation}\label{eq:totalIndexOfRefraction}
            \mathcal{N} = n + ik 
        \end{equation}
        This work will primarily focus on analyzing the real part of
        \cref{eq:totalIndexOfRefraction}, as it plays a crucial role in
        determining optical path differences and wavefront distortions in
        aero-optical applications. However, for completeness,
        \cref{fig:attenuationDB} presents the atmospheric attenuation at two
        different altitudes across a range of frequencies. The calculation of
        this attenuation requires a thorough understanding of the complex part
        of \cref{eq:totalIndexOfRefraction}, as it governs the absorption and
        energy dissipation mechanisms in the medium.
        \pic{1.0}{chapter1/attenuationDB}{Attenuation at different frequencies
        \cite{ITU2022, Richards2010}}{fig:attenuationDB}

        Understanding the effects of the environment in which an optical beam
        traverse is imperative in target detection. Radar engineers will be
        mainly concerned with the atmospheric environment (rain, clouds, fog,
        snow) but will not take much consideration on the impact aerodynamic
        effects such as shock wave and boundary layer interactions has on the
        optical beam. Some work showing how much the index of refraction is
        affected by aerodynamic effects has been performed by Gupta et.al.
        \cite{Gupta2020} for supersonic flows and showed that there is indeed,
        a change on index of refraction across a shock wave. For subsonic
        flows, it might be a valid assumption to ignore the aerodynamic effects
        on the optical beam; however for supersonic and specially for
        hypersonic flows this assumption has to be revisit. During a hypersonic
        flight the temperatures behind the shock are very high, that will no
        only induce thermal noise on the sensor but will also affect the
        electromagnetic properties that will influence the sensor's
        performance. Hence a higher distortion as well as power loss will be
        expected in a hypersonic flow. Being able to accurately understand this
        is of importance to build accurate sensors that can not only target
        objects moving at these speeds, but can also accurate predict targets
        from an object moving at hypersonic speeds.\\

        \Cref{fig:ch1AeroOpticsSchematic}, shows the path that a beam in a
        hypersonic flight will follow. The beam has to travel across the
        isolated gas, the radome, the boundary layer, shock layer and lastly
        environment. Traditionally, radar engineers ignore aerodynamic effects
        (shock waves, expansion waves) for their analysis; however for the case
        of hypersonic flights the aerodynamic effects cannot be ignored
        anymore, because the electromagnetic properties across the boundary
        layer and shock layer change. 
        \pic{0.8}{chapter1/aeroOpticsSchematic}{Optics Schematic}{fig:ch1AeroOpticsSchematic}

        Aero-optical investigations can be split into four quadrants as shown
        in \cref{tab:ch1AeroOpticalFidelities}. The optical parameters are
        contingent on the degree to which turbulence eddy resolution and
        turbulence fluctuations are captured in the \gls{CFD} simulation. In cases where a lower level of flow
        resolution is utilized, either a laminar flow or a \gls{RANS} simulation are employed as shown in Quadrants I
        and III of \cref{tab:ch1AeroOpticalFidelities}. While a RANS approach
        averages out turbulent fluctuations, it is a popular approach for
        hypersonic vehicle analysis due to it’s efficiency \cite{Candler2019}
        and can still provide aero-optical quantities such as \gls{GD}
        constant, polarizability, \gls{BSE}, \gls{OPL}, \gls{OPD}, and
        \gls{WD}. The amount of enthalpy is also an important criteria in the
        flow field. With high enthalpy flows, many physical phenomena in the
        flow field that are not present in low-speed flows present themselves.
        This includes nonequilibrium, reactive flows, and excitation of
        molecular internal modes, all of which can affect optical signals
        either directly or indirectly; these are shown in the top Quadrants.
        This work aims to develope an open-source \gls{AO} tool to investigate
        all quandrants. However, the results will be focus on Quadrants II and
        III.
        \input{aeroOpticsQuadrant}
    A conference paper focusing on Quadrant III was published by Liza et al. \cite{Liza2023}. In this paper, the authors examined the impact of high temperatures and nonequilibrium conditions on polarizability. Additionally, they investigated the effects of Mach number, turbulence, and chemistry modeling on optical properties, including the index of refraction and the dielectric constant of air.
