\chapter*{Abstract}
\glsreset{AO}
\glsreset{HAOT}
\glsreset{GD}
\glsreset{OPL}
\glsreset{OPD}
\glsreset{WD}
Hypersonic flows present unique challenges to measurements made by sensors
emitting electromagnetic waves due to the complex interplay between fluid
dynamics, thermodynamics, electrodynamics, atmospheric effects, and chemical
reactions in the surrounding environment. In particular, the thermal
nonequilibrium and turbulent nature of the flow field can cause both deflection
and degradation of optical signals as they traverse the boundary layer, shock
layer, and surrounding atmosphere.\\

A comprehensive physical understanding of these phenomena is necessary to
accurately assess and predict sensor performance in hypersonic environments.
While prior research in \gls{AO} has predominantly focused on low-speed or
low-enthalpy applications where perfect gas assumptions hold, this work
investigates the influence of real gas effects and thermal nonequilibrium in
high-enthalpy hypersonic flows. High-fidelity \gls{CFD} simulations are
employed to quantify the impact of these flow phenomena on optical signal
propagation.\\

Two representative cases are examined to explore different fidelity trade-offs:
(i) a low-enthalpy, high-flow-resolution case, and (ii) a high-enthalpy,
lower-flow-resolution case, where the modeling of chemical and thermal
nonequilibrium is critical. To facilitate the analysis of \gls{AO} 
distortions from \gls{CFD} results, an open-source Python package, \gls{HAOT},
was developed as part of this work. All results presented in this dissertation
were obtained using \gls{HAOT} version~v1.1.2. \\

This work advances the understanding of \gls{AO} in high-enthalpy flows 
by investigating the behavior of \gls{AO} properties in chemically and
thermally nonequilibrium gases. It also examines the influence of internal
energy level populations on \gls{AO} using a \gls{StS} approach. In addition,
this work includes the development of a computational package for analyzing
\gls{AO} in both high and low-enthalpy regimes under laminar and turbulent
flow conditions. The dissertation can be found in
\href{https://github.com/mliza/dissertation}{https://github.com/mliza/dissertation}, and the \gls{HAOT} package can be found in \href{https://haot.readthedocs.io/en/latest/}{https://haot.readthedocs.io/en/latest/}.

\newpage
