\chapter*{Acknowledgments}
Foremost, I would like to express my sincere gratitude to my adviser, Prof.
Kyle Hanquist, for his continuous support throughout my Ph.D. studies and
research, especially for his patience. I would also like to thank Prof. Wayne
Hacker at the UoA for his knowledge, guidance and support throughout this process, and
Prof. Ozgur Tumuklu at RPI for his help through this process. Additionally, I
am grateful to Prof. Brandon Chalifoux and Jerzy Rozenblit for his assistance during my Ph.D. journey. \\ 

A special thanks to the \textit{nerd-herd} for listening to me complain about
the UoA-AME department every other week. \\ 

A heartfelt thanks to my girlfriend, Cait, who stood by me and supported me
throughout this dissertation journey. She’s probably more relieved than I am to
finally see me finishing this degree—especially since she still thinks she can
turn me into a beach bum and outdoor enthusiast. Spoiler alert: It won't happen. \\

I would like to thank (or perhaps blame) my undergraduate adviser, Dean
Assimina (Mina) Pelegri at Rutgers University, for setting me on this path—and
for always showing me the tough love I needed to keep going instead of
quitting. Without her relentless push (and occasional eye rolls), I might have
given up long ago! \\

I would like to acknowledge Lawrence Livermore National Laboratory and the
Graduate Engineering Consortium for their partial funding of this
work. I am also grateful to my teams at Northrop Grumman Corporation and the
Johns Hopkins University Applied Physics Laboratory for providing the financial
support needed to complete this journey. In addition to financial support, I
would like to thank my colleagues at Northrop Grumman Corporation and the Johns
Hopkins University Applied Physics Laboratory for their encouragement and
support throughout the completion of this degree.\\

Lastly, I would like to express my gratitude to the many beer-tenders and
friends I made along my Ph.D. journey, as well as the breweries in Tucson
(Dragon Brewing Co., Pueblo Vida Brewing Co., Motosonora Brewing Co.) and in
Baltimore (Sapwood Cellars Brewing, Ministry of Brewing, CheckerSpot Brewing
Co., Heavy Seas Beer, Mobtown Brewing Company, Mystique Barrel Brewing and
Lager House) that provided the perfect stouts
and environments needed to complete this degree. 
