\chapter{Aero-Optics Tool\label{ch:chapter4}}
An open-source tool, \gls{HAOT}, has been developed to perform this analysis.
The tool is published on \href{https://pypi.org/project/haot/}{PyPI}, with its
source code hosted on \href{https://github.com/mliza/HAOT}{GitHub}, and
the documentation provided on \href{https://haot.readthedocs.io/en/latest/}{Read the Docs}. 
The current version of \gls{HAOT} includes five modules:

\begin{itemize} 
\item \textbf{Aerodynamics:} Implements commonly used aerodynamic functions.
\item \textbf{Optics:} Provides equations used in aero-optics and hypersonic
    flow analysis.
\item \textbf{Quantum Mechanics:} Offers commonly used quantum mechanical
    functions relevant to hypersonic flow.
\item \textbf{Constants:} Contains various constants, primarily
    spectroscopy-related used in optics.
\item \textbf{Conversion:} Provides a suite of conversion functions used in
    this module. 
\end{itemize}

Validation results are provided in subsequent sections. The constants and
conversion functions were validated through visual inspection. The primary
objective of \gls{HAOT} is to enable researchers to perform \gls{CFD} analysis
efficiently. Additionally, the tool is open for contributions, encouraging
other developers to expand its functionality. The goal is to create a
\textit{software blueprint} that can serve as a foundational tool for
researchers, particularly in academic \gls{CFD} settings, where software tools
are often poorly documented and developed \cite{Robillard1998,Liu2008}. 
\input{aerodynamics}
\input{optics}
\input{quantum_mechanics}
