\chapter{Conclusion\label{ch:ch6}} 
The study of \gls{AO} properties in hypersonic flow is a complex, multi-physics
problem. \Cref{fig:aoVennDiagram} illustrates the many different disciplines
involved in understanding \gls{AO} effects within hypersonic regimes. While
textbooks on each of these sub-disciplines are readily available, the true
challenge lies in synthesizing knowledge across these fields to achieve a
comprehensive understanding of \gls{AO} phenomena. This interdisciplinary
complexity is the motivation behind the development of the \gls{HAOT} package,
introduced in this dissertation, which enables \gls{AO} analysis based on
\gls{CFD} results.
\input{vennDiagram}

Although the results presented in this dissertation primarily focus on
Quadrants II and III of \Cref{tab:ch1AeroOpticalFidelities}, the \gls{HAOT}
package is designed to be extensible and capable of analyzing data from
Quadrants I and IV as well. In addition the \gls{HAOT} package follow good
coding practices. \\

In this work, high-enthalpy effects, such as nonequilibrium thermochemistry, on
\gls{AO} phenomena were investigated using high-fidelity computational
approaches. Investigations included a detailed investigation into
zero-dimensional problems that can be correlated to behind a normal shockwave
and vehicle scale simulations, where lower fidelity models are applied but at a
large spatial scale and with viscous effects. \\

This work adopted a state-resolved methodology within our thermochemical models to compute polarizability; this framework enables a detailed and accurate representation of how internal energy state populations affect the ensemble-averaged polarizability.
Specifically, numerical simulations were employed to assess the impact of
non-Boltzmann internal energy distributions on polarizability, a parameter that
plays a critical role in \gls{AO}. \\

For flow regimes in which strong thermochemical nonequilibrium is present—such as behind shock waves or in rarefied regions—the assumption of Boltzmann equilibrium breaks down. In such cases, the internal energy distributions deviate significantly from Boltzmann distributions.
But while the distributions vary, they are primarily different at the higher
level vibrationally excited levels that have significantly lower population
levels and have a minimal contribution to the overall polarizability.\\

The computational framework in this work is equipped to handle these scenarios,
although the primary focus of this study remains on characterizing trends and
sensitivities rather than presenting a comprehensive analysis of non-Boltzmann
effects. \\

This research also examined the relationship between the index of refraction
and the dielectric medium. The dense gas and dilute gas approaches produced
similar results, and the medium's dielectric constant can be approximated from
the index of refraction. The laminar case with frozen chemistry was found to
underpredict the index of refraction and the medium's dielectric constant due
to the under-prediction of the flow's density. Additionally, it was
demonstrated that turbulence affects the refraction index and the medium's
dielectric constant. It is also observed that the index of refraction and the
medium's dielectric constant have a higher impact on the stagnation line than
on the diagonal line; this is because the density increase across the shock is
much higher than in the boundary layer, this is because the shock creates a
high-density gradient which is not observed on the diagonal line. \\

In addition this work investigated turbulence effects at low speeds, this
investigation was need to develop the turbulence capabilities. 


%%%%%
\todo{Clean up and update conclusion}

In terms of future research areas that can be derived from this work, it is
recommended that the polarizability is not only treated as a function of signal
frequency but also as a function of temperature to gain a better understanding
of its behavior; this is because the damping factor, bond strength and
excitation frequency are functions of temperature and can not be assumed to be
constants.  \\

Investigating different species besides oxygen, especially nitric oxide which
is more polar compared to oxygen, would be an interesting study.  \\


%%%%% 



This work has touched the surface of the multyphysics nature of \gls{AO} in
hypersonic flows. This work has used state of the art open source solvers (SU2)
to investigate the effect of \gls{AO} in a hypersonic flow. This work has
showed that the chemestry composition is importnat because the polarizablity
will be affected by the chemestry composition of the gas. It has also showed
that for hypersonic flows, the \textit{frozen} flow assumption is not good
enough, and that nonequilibrium effect have to be considered. This work has
also shwod that for the cases investigated a $5$ species gas is a good
approximation, in practice \gls{AO} effects become importnat at low mach
numbers and low altitudes (terminal); and ioniation is importnat at high mach
number sand high altitudes (\Cref{fig:ch2flightSpeedAltitude}). In practices
for \gls{AO} applicatins, this is not a regime of big concern. 

