\section{Hypersonic Modeling\label{ch3:hypersonicModeling}}
In hypersonic flows, the fluid often no longer can be assumed to be in chemical and
thermal equilibrium \cite{Candler2019}. Consequently, the \gls{NS} equations must be
modified to account for nonequilibrium effects. \Cref{eq:navierStokesNoneq}
presents the multicomponent \gls{NS} equations, which involve $4N+19$ unknowns
\cite{Daily2018}.
\begin{subequations}\label{eq:navierStokesNoneq}
    \begin{align}
        &\continuityEins \label{eq:noneqSpeciesContinuity}\\
        &\noneqSpeciesContinuityEins \label{eq:noneqSpecies} \\
        &\noneqMomentumEins \label{eq:noneqMomentum} \\
        &\noneqEnergyEins \label{eq:noneqEnegy}
    \end{align}
\end{subequations}
The addition of the evolution of the mass of the chemical species $s$
\Cref{eq:noneqSpecies} gives the addition needed to account for chemical
reactions. As an example lets look at diatomic nitrogen:  
\begin{equation}\label{eq:diatomicNitrogen}
    \ce{N2 + M \rightleftharpoons N + N + M}
\end{equation}
The source term for the diatomic nitrogen is given on
\Cref{eq:diatomicNitrogenSourceTerm}
\begin{equation}\label{eq:diatomicNitrogenSourceTerm}
    w_{N_2} = -M_{N_2} \SqBracket{\frac{\rho_{N_2}}{M_{N_2}}
    \sum_{s}k_{f,s}\frac{\rho_s}{M_s} - \Parenthesis{\frac{\rho_N}{M_N}}^2 \sum_{s}
    k_{b,s}\frac{\rho}{M_s}  }
\end{equation}
Usually the dissociation rate is computed from a temperature-dependent
\textit{Arrhenius} reaction rate, and the combination rate is set so that the
source term is zero in thermodynamic equilibrium \cite{Candler2019}.  \\

The total energy term in \Cref{eq:noneqEnegy} can be decomposed as: 
\begin{equation}\label{eq:totalDecomposedNoneqEnergy}
    E = \sum_s \rho_s\Parenthesis{e_{tr,s} + e_{int,s} + h_s^{o} } +
    \frac{1}{2}\rho u_k u_k
\end{equation}

The multicomponent \gls{NS} equations can be solved using some of the models:
\begin{itemize}
    \item \textbf{Single-temperature $(1T)$ models:} All energy modes
        (translational, rotational, vibrational and electronic) are in
    equilibrium and are described by a single temperature. Low fidelity, low
        computational cost.  
    \item \textbf{Two-temperature $(2T)$ models:} These models treat the
        vibrational energy separately, assuming rotational and translational
        energy equilibrates faster than vibrational energy. Medium fidelity,
        low computational cost.
    \item \textbf{Multi-temperature $(nT)$ models:} These models describe each
        energy level with a different temperature. High fidelity, medium computational cost.
    \item \textbf{State to state $(StS)$ models:} Solves the governing
        equations coupled to the master equation that accounts for the
        state-to-state transition \cite{Josyula2017}. Highest fidelity, highest
        computational cost \cite{Hanquist2020}.
\end{itemize}

\subsection{Two-Temperature}
The two-temperature $(2T)$ approach is one of the most commonly used models for
the analysis of hypersonic flows, particularly in the context of high-enthalpy
nonequilibrium gas dynamics relevant to hypersonic vehicle design. Among
various formulations, the Park two-temperature model \cite{Park1989} is widely
adopted due to its balance between physical fidelity and computational
efficiency. \\

In the $2T$ framework, thermal nonequilibrium between different molecular
energy modes is captured by introducing two distinct temperatures. One
temperature characterizes the translational and rotational energy modes of the
gas molecules (collectively referred to as the kinetic temperature), while a
second temperature accounts for the vibrational and electronic energy modes
(often referred to as the vibrational-electronic temperature). This separation
enables the model to describe the delayed excitation and relaxation phenomena
that occur during high-speed, high-temperature flows, especially in
shock-dominated regions or boundary layers of hypersonic vehicles. \\

The evolution of the internal vibrational energy is described by the
\textit{Landau-Teller} \cite{Hanquist2020} relaxation equation:
\begin{equation}\label{eq:landauTeller}
\frac{d\mathcal{E}_{vib}}{dt} = \frac{\mathcal{E}_{vib, 0} -
    \mathcal{E}_{vib}}{\tau_{vib}}
\end{equation}
where $\mathcal{E}_{vib, 0}$ is the vibrational energy at equilibrium, and
$\tau_{vib}$ is the characteristic vibrational relaxation time. The value of
$\tau_{vib}$ can be obtained by various methods; the most common approach is
based on the Millikan-White correlation for relaxation time
\cite{Millikan1963}, which accounts for both temperature and molecular species
effects.\\

\Cref{eq:millikanWhite} provides the vibrational relaxation time formula:
\begin{equation}\label{eq:millikanWhite}
    \tau_{vib} = \frac{1}{p} \exp\Parenthesis{ AT^{1/3} - B} 
\end{equation}
Where: $A$ and $B$ are empirical constants dependent on gas species. \\

The chemical kinetics are captured through temperature-dependent reaction rates, commonly expressed using \textit{Arrhenius}-type rate coefficients:
\begin{equation}\label{eq:arrheniusRates}
k_d = A e^{- \beta E_a }
\end{equation}
where $A$ is a pre-exponential factor, $\beta$ is the thermodynamic beta, and $E_a$ is the activation energy for the dissociation or reaction process. These reaction rates govern the time scales of chemical nonequilibrium and are essential for modeling high-temperature reacting flows in hypersonic regimes.

\subsection{\acrfull{StS}}
The \gls{StS} approach is a higher-fidelity model used to describe energy
transfer in nonequilibrium gas dynamics. In contrast to the $2T$ model,
\gls{StS} directly simulates the population of each discrete internal energy
state, such as individual vibrational and electronic levels. These populations
evolve according to a system of master equations, which account for energy
exchange between states due to collisional and radiative processes.\\

obtained through quantum chemistry methods such as quasi-classical trajectory
(\gls{QCT}) calculations \cite{Andrienko2017,Chaudhry2019}, or through more
generalized semi-empirical models like the forced harmonic oscillator
(\gls{FHO}) approach \cite{Adamovich1998a}. These methods are computationally
expensive. They capture excitation, de-excitation, dissociation, and
recombination processes at the level of individual energy states, enabling
detailed resolution of thermochemical nonequilibrium phenomena that are
inaccessible to lower-fidelity models.\\

Forward reaction rates are calculated by \gls{QCT} or \gls{FHO}, both of which
provide state-specific transition probability. Backward reaction rates are
determined via detailed balance.\\ 

The Master equation given in \Cref{eq:masterEquation} for the \gls{StS} model account for conservation of
momentum and trans-rotational energy as well as for number density of the
individual vibrational states \cite{Kim2013}.
\begin{equation}\label{eq:masterEquation}
\frac{dN_v}{dt} = \sum_s\Parenthesis{ R_{v,s}N^2_ON_s - D_{v,s}N_vN_s} +
    \sum_s\Parenthesis{K_{v^{\prime}, v} N^{\prime}_{v}N_s -
    K_{v,v^{\prime}}N_vN_s  }, \;\;\;\; v = 0, ..., v_{max}
\end{equation}
where: $R_{v,s}$ and $D_{v,s}$ are the state specific recombination and
dissociation rates. \\

Diatomic molecules such as \ce{N2} and \ce{O2} have multiple vibrational energy
levels. Instead of treating each molecule as a single species with uniform
behavior, each vibrational level can be considered almost like its own
\textit{pseudo-species} because molecules in different vibrational states
behave differently in chemical reactions and energy exchange processes.

\subsection{High-Enthalpy \gls{CFD}}
To numerically solve the nonequilibrium governing equations incorporating these
thermochemical effects, the open-source \gls{CFD} solver \Gls{SU2} \Gls{NEMO}
\cite{Maier2021,Maier2023a} is used. \Gls{SU2}--\Gls{NEMO} extends the \Gls{SU2}
framework to model continuum flows in thermochemical nonequilibrium by solving
the multicomponent Navier–Stokes equations with appropriate source terms for
chemical reactions and internal energy relaxation. These equations are
expressed compactly in conservation form in
\Cref{eq:nonequilibriumGoverningEqConservativeA} and expanded component-wise in
\Cref{eq:nonequilibriumGoverningEqConservativeB}. The solver incorporates
detailed thermodynamic models, finite-rate chemical kinetics, and energy
exchange mechanisms, making it suitable for predicting both fluid dynamic and
optical properties in hypersonic environments. 
\begin{equation}\label{eq:nonequilibriumGoverningEqConservativeA}
    \nonequilibriumGoverningEqConservativeA
\end{equation}

\begin{equation}\label{eq:nonequilibriumGoverningEqConservativeB}
    \ScaleMath{0.72}{\nonequilibriumGoverningEqConservativeB}
\end{equation}
where $\mathcal{U}$ are the conservative variables, $\mathcal{F}^c$ are the
convective fluxes, $\mathcal{F}^{v}$ are the viscous fluxes, and $\mathcal{Q}$
source terms. \\

\Gls{SU2}--\Gls{NEMO} uses a rigid-rotor harmonic oscillator two-temperature
model to calculate the thermodynamic state. The total energy and
vibrational-electronic energy per unit volume are given in \Cref{eq:nemoEnergy}.
\begin{subequations}\label{eq:nemoEnergy}
    \begin{align}
        &\rho e = \sum_{s}\rho_s\Parenthesis{e_s^{tr} + e_{s}^{rot} + e_s^{vib} + e_s^{el}
        + e^0_s + \frac{1}{2}\bm{u}^T\bm{u}} \label{eq:nemoTotalEnergy} \\
        &\rho e^{ve} =\sum_s \rho_s \Parenthesis{e_s^{vib} + e_s^{el} }
        \label{eq:nemoVibrationalEnergy} 
    \end{align}
\end{subequations}

Where:
\begin{equation}\label{eq:nemoTranslationalSpeciesEnergy}
    e^{tr}_s = \begin{cases}
        \frac{3}{2}\frac{R T}{M_s} & \text{monatomic and polyatomic species} \\
        0 & \text{electrons}
    \end{cases}
\end{equation}

\begin{equation}\label{eq:nemoRotationalSpeciesEnergy}
    e^{rot}_s = \begin{cases}
        \frac{\zeta}{2}\frac{R T}{M_s} & \text{polyatomic species} \\
        0 & \text{electrons and monatomic species}
    \end{cases}
\end{equation}
where $\zeta$ is an integer specifying the number of axes of rotation
\begin{equation}\label{eq:nemoVibrationalSpeciesEnergy}
    e^{vib}_s = \begin{cases}
        \frac{R}{M_s}\frac{\theta_s^{vib}}{exp(\theta_s^{vib}/T_{vib}) -1}  & \text{polyatomic species} \\
        0 & \text{electrons and monatomic species}
    \end{cases}
\end{equation}
where $\theta_s^{vib}$ is the characteristic vibrational temperature of the
species
\begin{equation}\label{eq:nemoElectronicSpeciesEnergy}
    e^{el}_s = \begin{cases}
        \frac{R}{M_s}\frac{\sum_{i=1} g_{i,s}\theta_{i,s}^{el}exp\Parenthesis{
            -\theta_{i,s}^{el}/T_{vib}}}{\sum_{i=0}g_{i,s}exp\Parenthesis{-\theta_{i,s}^{el}/T_{vib}}}  &
        \text{polyatomic and monatomic species} \\
        \frac{3}{2}\frac{RT_{vib}}{M_s} & \text{electrons}
    \end{cases}
\end{equation}
where $\theta_s^{el}$ is the characteristic electronic temperature of the
species and $g_i$ is the degeneracy of the $i$th state. \\

The vibrational relaxation is computing using the \textit{Landau-Teller}
relaxation time with \textit{Park}\cite{Park1989} high energy correction and it
is given in \Cref{eq:vibrationalRelaxation}
\begin{equation}\label{eq:vibrationalRelaxation}
    \dot{\Theta}^{tr:vib} = \sum_s \rho_s \frac{de_s^{vib}}{dt} =
    \sum_s\rho_s\frac{e_s^{vib*} - e_s^{vib}}{\tau_s}
\end{equation}
