\section{Turbulence Modeling\label{ch3:turbulenceModeling}}

If we take the \gls{NS} \cref{eq:navierStokesEquationsEins} and applied a
Reynolds decomposition \cref{eq:reynoldsDecomposition}
\begin{subequations}\label{eq:navierStokesEquationsEins}
    \begin{align}
        \continuityEins \label{eq:continuityEins}\\
        \momentumEins \label{eq:momentumEins} \\
        \energyEins \label{eq:energyEins}
    \end{align}
\end{subequations}





\begin{equation}\label{eq:reynoldsDecomposition}
    u = \overline{u} + u^{\prime}
\end{equation}

You will end with the \gls{RANS} equations given on 
\begin{subequations}\label{eq:reynoldsAverageNavierStokesEquations}
    \begin{align}
        &\ransContinuityEins \label{eq:ransContinuity}  \\
        &\ransMomentumEins \label{eq:ransMomentum}   \\
        &\ransEnergyEins \label{eq:ransEnergy}
    \end{align}
\end{subequations}




The history of turbulence modeling is intertwined with the development of fluid
dynamics and computational power. 

In $1925$ Prandtl introduced the mixing length model (an analogy to the mean free
path in a gas). Model's bases in the mixing length hypothesis referred to as an
algebraic model or a zero-equation model of turbulence. In $1945$ Prandtl
assumed a model in which the eddy viscosity depends upon the kinetic energy of
the turbulent fluctuations, and proposed a partial differential equation to
solve for the kinetic energy (this is a one-equation model).


By definition, an n-equation model signifies a model that requires solution of n additional differential transport equations in addition to expressing conservation of mass, momentum and energy for the mean flow.


In $1942$ Kolmogorov introduced a first complete model of turbulence, in
addition to having a modeled equation for the kinetic energy $\kappa$, he introduced a
second parameter $\omega$. This is a two-equation model of turbulence.

Chou $(1945)$ and Rotta $(1951)$ laid the foundation of turbulence models that
avoid the used of the Boussinesq Approximation. Model for the differential
equation governing evolution of the tensor that represents turbulent stresses,
such models are most appropriately described as stress transport models. Many
authors refer to this approach as a second order closure or second moment
closure. The primary conceptual advantage of a stres transport model is the
natural manner in which nonlocal and history effects are incorporated.

For a three-dimensional flow, a stress-transport model introduces seven
equations, one for the turbulence (length or equivalent) scale and six for the
components of the Reynolds-stress tensor.


\todo{Clean up section avobe}



In $1963$, Smagorinsky \cite{Smagorinsky1963} introduced the \gls{LES} model to
simulate atmospheric air currents. The \gls{LES} framework is grounded in the
energy cascade model developed by Kolmogorov in the $1940$s, which itself
builds upon the earlier work of Richardson. The fundamental concept behind
\gls{LES} is to explicitly compute the large-scale motions, which are
influenced flow geometry and are not universal, up to a prescribed length
scale. The smaller scales, which tend to exhibit more universal
characteristics, are modeled using a \gls{SGS} model \cite{Pope2000}.\\

This separation between larger and smaller scales is typically achieved by
spatially filtering the velocity field using a kernel \cite{Leonard1975}. The
convolution kernel effectively splits the flow field into resolved large scales
and modeled \gls{SGS} components in an \gls{LES} framework. Developing
physically realistic \gls{SGS} models requires a comprehensive understanding of
both the physics and statistical properties of scale interactions between large
and small scales in turbulent flows. \gls{SGS} modeling is traditionally
predicated on the hypothesis that if subgrid scales exist, the flow is locally
turbulent in both space and time \cite{Garnier2009}.\\

There are two primary \gls{SGS} modeling strategies:
\begin{itemize}
    \item \textbf{Functional modeling:} This approach focuses on the energetic
        impact of subgrid scales on resolved scales. It assumes that balancing
        energy transfer between scale ranges is sufficient to describe the
        subgrid-scale effects. Functional models often neglect backscattering,
        i.e., energy transfer from smaller scales back to larger scales
        \cite{Burton2005}.
    \item \textbf{Structural modeling:} This strategy attempts to reconstruct
        subgrid-scale information directly by generating a new field from the
        filtered field (e.g., velocity, density) that better approximates the
        unfiltered field. Structural models account for backscattering because
        they aim to reconstruct small-scale structures within the
        flow \cite{Burton2005}.
\end{itemize}

Functional models commonly represent the \gls{SGS} stress tensor (Reynolds
stress tensor) using eddy-viscosity closures. However, this approach linearizes
the inherently nonlinear stress tensor, leading to the loss of some physical
details. It is important to note that the famous closure problem originates
from the convective terms in the \gls{NS} equations. Additionally, functional
models are often criticized for being overly dissipative due to their nature of
transferring energy from larger to smaller scales while failing to capture
backscattering effects. In contrast, structural models incorporate
backscattering and are typically nonlinear, allowing for a more accurate
representation of small-scale flow structures.

\todo{Missing turbulence modeling}
