\chapter{Conclusion\label{ch:ch5}} 
\glsreset{CFD}
\glsreset{AO}
\glsreset{HGV}
\glsreset{ICBM}
\glsreset{HAOT}
\glsreset{EM}
\glsreset{QM}
\glsreset{GD}
\glsreset{StS}
The study of \gls{AO} properties in hypersonic flows is inherently a complex, multi-physics problem.
\Cref{fig:aoVennDiagram} illustrates the wide range of disciplines—such as
compressible flows, turbulence, \gls{EM}, and \gls{QM} that must be 
integrated to fully understand and characterize \gls{AO} effects in
hypersonic regimes. While comprehensive textbooks and resources exist for each
of these individual sub-disciplines, the true challenge lies in synthesizing
their principles into a unified package capable of capturing the coupled,
nonlinear nature of \gls{AO} phenomena. 
\input{vennDiagram}

This interdisciplinary complexity provided the motivation for the development
of the \gls{HAOT} package, introduced in this dissertation, which enables
high-fidelity \gls{AO} analysis directly from \gls{CFD} results. The package
bridges the gap between computational fluid simulations and optical wavefront
characterization, offering a practical and extensible package for the study of
\gls{AO} effects under turbulent and hypersonic flow conditions. \\

The results presented in this dissertation primarily focused on
Quadrants II and III in \Cref{tab:ch1AeroOpticalFidelities}, the \gls{HAOT}
package is designed to be extensible and capable of analyzing data from
Quadrants I and IV as well. In addition, the \gls{HAOT} package follows good
coding practices and standards, with proper testing and extensive
documentation. \\

In this work, high-enthalpy effects—such as nonequilibrium thermochemistry—on
\gls{AO} phenomena were investigated using high-fidelity computational
approaches. This investigation included a detailed study of three
fidelities of the \gls{GD} constant (\Cref{fig:gdFidelities}). The original
research question—\textit{To what extent do high-enthalpy flow conditions
influence the \gls{AO} properties of the medium?}—was addressed by performing
multiple \gls{CFD} simulations. \\

The first part of this work (\Cref{sec:lowFidelity}) focused on low-fidelity
enthalpy resolution by assuming a temperature-dependent \gls{GD} and
high-fidelity flow resolution using a \gls{LES} simulation at subsonic $(1L)$
and supersonic $(2L)$ speeds. The \gls{AO}
properties were evaluated by computing the polarizability for air using the
Kerl extrapolation method \cite{Kerl1992}. \\

The results showed that \gls{AO} properties—such as the medium’s permittivity,
index of refraction, and electric susceptibility—are not only
temperature-dependent but also wavelength-dependent, even at low enthalpy
conditions. Additional parameters, including \gls{WD}, \gls{OPL}, and \gls{OPD}, were also
computed. These additional \gls{AO} effects arise from spatiotemporal
fluctuations in the flow field, which can distort optical wavefronts. Such
effects cannot be captured by steady-state or \gls{RANS}-type approaches,
thereby motivating the use of \gls{LES} to resolve the unsteady, turbulent
structures responsible for these optical distortions. \\

The second study in this work (\Cref{sec:medFidelity}) focused on
medium-fidelity enthalpy resolution by using species-specific \gls{GD}
modeling. This fidelity level included both a zero-dimensional (heat bath)
study and a two-dimensional (IRV2-vehicle) flow study. The heat bath
configuration was employed due to its lower computational cost, while the
IRV2-vehicle geometry was selected as a more realistic aerodynamic shape.\\

For the zero-dimensional cases, two investigations were performed. The first
examined the effect of varying gas composition, and the second compared a
five-species model with an eleven-species model. The gas composition study
showed that, for the terminal phase of flight, the amount of \ce{N2} has the
largest influence on the \gls{GD}, which in turn strongly affects the \gls{AO}
properties. Additional cases using standard air composition at different
pressures (Cases $4C$ and $5C$) were also analyzed. These results demonstrated
that increased pressure impacts \gls{AO} properties due to enhanced molecular
dissociation. \\

The second part of the zero-dimensional study compared a five-species gas mixture with an
eleven-species mixture. Under the investigated conditions representative of the
terminal phase of flight, the low mass fractions of the additional species in
the eleven-species case did not significantly influence the overall \gls{AO}
properties. This indicates that, in this regime, the dominant contributions to
the optical characteristics are governed primarily by the major species, with
minor species playing a negligible role.\\

A two-dimensional flow simulation was also performed for the medium-fidelity
enthalpy case. As expected, the highest thermal effects were observed along
the stagnation line—an important region for optical sensors or seekers on
hypersonic vehicles. This finding further highlights the utility of
zero-dimensional cases, such as the heat bath configuration, due to their low
computational cost while still capturing key trends. Additionally, the results
showed that chemical nonequilibrium has an impact on the \gls{AO}
properties, with frozen-flow models underpredicting these effects.\\

The third fidelity examined in this work involved high-fidelity enthalpy cases
(\Cref{sec:highFidelity}) using internal-state-specific, species-specific
\gls{GD}. In this section, a \gls{StS} methodology was employed to compute
polarizability. The results showed that the Boltzmann method overpredicts
polarizability, which in turn leads to an overestimation of additional \gls{AO}
properties.\\

For flow regimes with strong thermochemical nonequilibrium—such as regions
behind shock waves or in rarefied zones—the assumption of Boltzmann
equilibrium breaks down. In such cases, internal energy distributions deviate
significantly from the Boltzmann form. However, while these distributions vary,
the deviations occur primarily in higher vibrational levels, which are sparsely
populated and contribute minimally to the overall polarizability. \\

The computational package developed in this work is equipped to handle such
non-Boltzmann scenarios. Nonetheless, the primary focus remains on
characterizing trends and sensitivities rather than delivering a fully
comprehensive treatment of non-Boltzmann effects.  \\

The central research question—\textit{To what extent do high-enthalpy flow
conditions influence the \gls{AO} properties of the medium?}—was directly
addressed in this work. The results show that high-enthalpy effects, including
vibrational excitation, chemical nonequilibrium, and variations in species
composition, do alter the \gls{AO} properties of the medium. These processes
modify the polarizability of the gas, which in turn changes the index of
refraction experienced by optical waves propagating through the flow. However,
for the conditions studied here (terminal phase of flight), these effects are minimal. The analysis
focused on low-hypersonic flight regimes in which additional molecular degrees
of freedom become active, but where the overall density remains relatively low.
\\

This regime is particularly relevant for hypersonic vehicles such as
\glspl{HGV} and \glspl{ICBM}, which would benefit from \gls{Lidar} systems or
other active optical seekers. Such systems typically operate only during the
terminal phase of flight, when the vehicle is closest to the target, traveling
through higher-density atmospheric regions but at reduced Mach numbers compared
to midcourse flight. These conditions define the operational window in which
\gls{AO} effects must be accurately characterized to ensure seeker
performance.\\


\Cref{tab:summaryGD} provides the summary of the \gls{GD} constants calculated
in \cref{sec:gasComposition,ch4:speciesStudy,ch4:frozenVsNonequilibrium} at the
point at which the flow reached chemical equilibrium.
\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
$ \;$ & $4C$ & $5C$ & $1S1$ & $2S1$ & $1R$ & $2R$ & $3R$ \\
\hline
$GD \times 10^{-4}\UnitsFrac{kg}{m^3}$ & $2.254$ & $2.255$ & $2.290$ &
$2.255$ & $2.256$ & $2.269$ & $2.307$ \\
\hline
$Error \;\%$ & $0.356$ & $0.401$ & $1.960$ & $0.445$ & $0.445$ &
$1.020$ & $2.720$ \\
\hline
\end{tabular}
\caption{Summary of \acrlong{GD} for studied
cases}\label{tab:summaryGD}
\end{center}
\end{table}
As previously shown in \cref{sec:diluteVsDense}, the dilute-medium formulation of the index of refraction remains
valid for high-enthalpy flows. Thus, \cref{eq:gladstoneDaleRelationship} can be
used as an alternative approximation for the index of refraction, instead of
the polarizability formulation \cref{eq:diluteRefractiveIndex}. The \gls{GD}
for air composed of $79\%$ $\ce{N2}$ and $21\%$ $\ce{O2}$ at
standard sea-level atmospheric conditions is
$2.246\times10^{-4}\UnitsFrac{kg}{m^3}$. This value serves as the reference
\gls{GD} against which the calculated values are compared. \\

For the terminal phase of flight, the difference between the sea-level
\gls{GD} and the one obtained from nonequilibrium chemistry simulations is
small, indicating that compositional changes due to high-enthalpy effects do
not drastically alter the optical properties of the medium in this regime.\\

The largest deviation from the reference value is less than $3\%$, observed at
the highest Mach number considered in this study,
$M = 15.2\Units{\;}$—a value significantly higher than what would typically be
expected during terminal flight conditions. This suggests that, for realistic
terminal-phase Mach numbers, the calculated \gls{GD} and the standard air
\gls{GD} remain in very close agreement, supporting the use of the standard
value for practical \gls{AO} predictions in these scenarios. \\

Accurately accounting for these variations is essential for the design and
performance assessment of optical systems in hypersonic vehicles. However, the
present results show that, for the low-hypersonic regimes
investigated—particularly those relevant to terminal flight
conditions—high-enthalpy effects contribute minimally to the overall \gls{AO}
impact. This suggests that, under similar conditions, simpler modeling
approaches may be sufficient without sacrificing accuracy. Nevertheless, the
modeling framework developed here retains the capability to incorporate
high-enthalpy effects into high-fidelity \gls{AO} simulations when required.
This flexibility provides a means to evaluate and mitigate potential \gls{AO}
impacts under more extreme hypersonic flight conditions, thereby supporting
informed sensor and seeker design decisions.


\input{futureWork}
