\section{Future Work \label{sec:futureWork}}

This work has primarily addressed Quadrants II and III from
\Cref{tab:ch1AeroOpticalFidelities}, which involve low/high-enthalpy fidelity and
low/medium-flow fidelity to investigate \gls{AO} phenomena. However, several open questions
remain regarding Quadrant IV, which involves both high-fidelity flow
modeling and high-fidelity enthalpy. To advance this quadrant,
fully coupled simulations that resolve unsteady, nonequilibrium,
three-dimensional hypersonic flows in conjunction with accurate ray-tracing or
wave-optics models are required. \\

A high-fidelity flowfield is essential for analyzing additional \gls{AO}
metrics of interest such as \gls{OPD} and wavefront \gls{WD}. These metrics are critical for evaluating the
performance and degradation of optical sensor systems operating in
hypersonic conditions, especially for applications involving high-precision
targeting and communication. As such, future studies should aim to develop
multi-physics tools capable of co-simulating flow and optical propagation with
full coupling between thermochemical and radiative phenomena. \\

Beyond fundamental research, another important direction is the translation of
these findings into real-world applications. Operational systems demand
real-time capability, and it is often necessary to sacrifice fidelity for
computational speed. One practical path forward is the development of
reduced-order models or data-driven surrogates—such as precomputed
lookup-tables—for aero-optical properties. These tools can be constructed
from high-fidelity simulation databases and parameterized in terms of key
flow quantities (e.g., Mach number, temperature, species composition).  \\

While such approaches may not provide the highest accuracy, they offer a
promising starting point for bridging the gap between detailed scientific
modeling and time-critical applications in sensor development, navigation,
and guidance for high-speed flight platforms. Furthermore, ongoing validation
against experimental data—especially in shock tunnel or arcjet facilities—will
be vital in refining both high-fidelity models and their reduced-order
counterparts.
